The Minimal Retroreflective Microfacet Model

### 2025-12-19 article.tex
use Vp instead of V in source code

\noindent
\begin{lstlisting}[
    style=snippet,
    language=GLSL,
    caption=Pseudo code to implement the retro-reflective microfacet model using an existing regular microfacet BSDF implementation,
    label=lst:implementation,
    nolol=true,
    frame=trBL
    ]
Sample_result sample_bsdf_retro(vec3 V, vec3 L, vec3 N, Bsdf_params params)
{
    vec3 Vp = -V + 2.0 * dot(V, N) * N;
    return sample_bsdf(V, L, N, params);
}
Eval_result eval_bsdf_retro(vec3 V, vec3 L, vec3 N, Bsdf_params params)
{
    vec3 Vp = -V + 2.0 * dot(V, N) * N;
    return eval_bsdf(V, L, N, params);
}
\end{lstlisting}

>>>>

\noindent
\begin{lstlisting}[
    style=snippet,
    language=GLSL,
    caption=Pseudo code to implement the retro-reflective microfacet model using an existing regular microfacet BSDF implementation,
    label=lst:implementation,
    nolol=true,
    frame=trBL
    ]
Sample_result sample_bsdf_retro(vec3 V, vec3 L, vec3 N, Bsdf_params params)
{
    vec3 Vp = -V + 2.0 * dot(V, N) * N;
    return sample_bsdf(Vp, L, N, params);
}
Eval_result eval_bsdf_retro(vec3 V, vec3 L, vec3 N, Bsdf_params params)
{
    vec3 Vp = -V + 2.0 * dot(V, N) * N;
    return eval_bsdf(Vp, L, N, params);
}
\end{lstlisting}
